Investigating Determinism of Physics Engines for usage in CAV and V\&V simulations

### 2021-04-19 document/source/body.tex
simplified

\subsection{Actor Navigation}
There is existing evidence to suggest actor navigation, typically pedestrians, could be a source of non-deterministic simulation behaviour~\cite{CARLABenchmark}. Unreal Engine is the underlying framework for the CARLA simulator which uses the A* search algorithm to find optimal paths for actor navigation~\cite{newton2016unreal}. The optimality and validity of A* solutions is only guaranteed if the environment is deterministic, and if not, then there are no guarantees that an execution of the same A* solution will lead to the same outcome across multiple runs.

>>>>

\subsection{Actor Navigation}
There is evidence to suggest actor navigation, typically pedestrians, could be a source of non-deterministic simulation behaviour~\cite{CARLABenchmark}. Unreal Engine is the underlying framework for the CARLA simulator which uses the A* search algorithm to find optimal paths for actor navigation~\cite{newton2016unreal}. The optimality and validity of A* solutions is only guaranteed if the environment is deterministic, and if not, then there are no guarantees that an execution of the same A* solution will lead to the same outcome across multiple runs.
